Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
adding captions

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.47\linewidth}
		\centering
		\raisebox{.2\textwidth}{%
		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
		}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}[t]{0.43\linewidth}
		\centering
	%	\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{fig:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart (b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
\end{figure}

@@

Basin A and Basin B are two configurationally metastable basins. 
We hesitate to classify the basins as separate phases. We hypothesize
that Basin B is present at higher temperatures. This is evidenced by
a simulation of a system in Basin A whose temperature was linearly
ramped from 280K to 340K over 100 ns. Visually, there is a distinct
change in pore structure from one characteristic of Basin A 
(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
three easily measurable order parameters: the distance between pores,
the membrane the thickness and the ratio of pore radius to the uncertainty
in pore radius. The distance between pores was measured as described 
previously. The membrane thickness was measured using the length of the
z box vector. The pore radius was measured by calculating the distance
between the center of mass of each aromatic ring and the center of mass
of all aromatic rings in respective pores. The pore radius is divided by
its uncertainty in order to understand the degree to which monomers 
obstruct the pore region. Referring back to our temperature ramped system,
the slope of all order parameters change around 310K 
(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
possibility of an abrupt change in system ordering. To prove that the 
basins are in fact two different phases, we must observe evidence of a
first order phase transition, which would be indicated by a discontinuity
in an order parameter as a function of temperature. Our 100 ns temperature
ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
hysteresis, we performed a slow, stepwise temperature ramp. Starting from
structures equilibrated at 280K, the system temperature was raised to 
300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
temperature was raised 5K and equilibrated again for 200 ns. We repeated
this process until the system was equilibrated for 200 ns at 320K. In all
cases, we observed smooth changes in order parameters as temperature was
increased implying that we have not found two phases 
(Figure~\ref{fig:phase_transition}).

@@

                \caption{}\label{fig:thickness_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{order_tramp.png}
                \caption{}\label{fig:order_tramp}
        \end{subfigure}
        \caption{}\label{fig:tramp}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_layered.png}
		\caption{}\label{fig:p2p_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{thickness_layered.png}
		\caption{}\label{fig:thickness_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{order_layered.png}
		\caption{}\label{fig:order_layered}
	\end{subfigure}
\end{figure}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sanwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses the highest degree of layer partitioning.}\label{fig:zdf}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.47\linewidth}
		\centering
		\raisebox{.2\textwidth}{%
		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
		}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}[t]{0.43\linewidth}
		\centering
	%	\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{fig:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating features less than 1 nanometer apart. (b) 1D small angle X-ray scattering indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
\end{figure}

@@

Basin A and Basin B are two configurationally metastable basins. 
We hesitate to classify the basins as separate phases. We hypothesize
that Basin B is present at higher temperatures. This is evidenced by
a simulation of a system in Basin A whose temperature was linearly
ramped from 280K to 340K over 100 ns. Visually, there is a distinct
change in pore structure from one characteristic of Basin A 
(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
three easily measurable order parameters: the distance between pores,
the membrane the thickness and the ratio of pore radius to the uncertainty
in pore radius. The distance between pores was measured as described 
previously. The membrane thickness was measured using the length of the
z box vector. The pore radius was measured by calculating the distance
between the center of mass of each aromatic ring and the center of mass
of all aromatic rings in respective pores. The pore radius is divided by
its uncertainty in order to understand the degree to which monomers 
obstruct the pore region. Referring back to our temperature ramped system,
the slope of all order parameters change around 315K - 325K 
(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
possibility of an abrupt change in system ordering. To prove that the 
basins are in fact two different phases, we must observe evidence of a
first order phase transition, which would be indicated by a discontinuity
in an order parameter as a function of temperature. Our 100 ns temperature
ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
hysteresis, we performed a slow, stepwise temperature ramp. Starting from
structures equilibrated at 280K, the system temperature was raised to 
300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
temperature was raised 5K and equilibrated again for 200 ns. We repeated
this process until the system was equilibrated for 200 ns at 320K. In all
cases, we observed smooth changes in order parameters as temperature was
increased implying that we can not yet claim the existence of two phases (Figure~\ref{fig:phase_transition}).
The same process will continue to be repeated up to 340K in the near future
since we have not surpassed the temperatures where we observe abrupt slope 
changes in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).

@@

                \caption{}\label{fig:thickness_tramp}
        \end{subfigure}
        \begin{subfigure}[b]{0.325\textwidth}
                \centering
                \includegraphics[width=\textwidth]{order_tramp.png}
                \caption{}\label{fig:order_tramp}
        \end{subfigure}
        \caption{(a) The open pore structure exhibited by a structure equilibrated
	at 280K is characteristic of Basin A. (b) The closed pore structure with 
	a high degree of radial disorder exhibited when the structure in (a) is 
	heated to 340K is characteristic of Basin B. (c) A plot of distance between pores
	vs. temperature changes slope near 325K. (d) A plot of membrane thickness vs. 
	temperature changes slope near 325K. (e) The plot of the ratio of pore radius to
	its uncertainty changes slope near 315K.}\label{fig:tramp}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_layered.png}
		\caption{}\label{fig:p2p_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{thickness_layered.png}
		\caption{}\label{fig:thickness_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{order_layered.png}
		\caption{}\label{fig:order_layered}
	\end{subfigure}
	\caption{(a) }\label{fig:phase_transition}
\end{figure}
